---
title: "Introduction to BayesMEModel"
output: 
  rmarkdown::html_vignette:
    fig_path: "vignettes/"
vignette: >
  %\VignetteIndexEntry{Introduction to BayesMEModel}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(BayesMEModel)
```

## Introduction to the package

The `BayesMEModel` R package presents a comprehensive suite of functions tailored to fitting Bayesian regression models and performing statistical analyses. Seamlessly integrated with Stan models, the package encompasses Linear Regression, Logistic Regression, as well as their corresponding measurement error correction models. Additionally, the package includes utilities designed to assist in the estimation of specific parameters, thereby enhancing the accuracy of estimates. `BayesMEModel` contains the following main functions: 

* `fit_linear_regression` and `fit_logistic_regression`

  - Required Inputs:
    + **model**: Compiled Stan model for Linear Regression or Logistic Regression.
    + **N**: Number of observations.
    + **D**: Number of input variables.
    + **x**: Independent variable of dimension N by D.
    + **y**: Dependent variable.
  
  - Purpose: This function fits the provided Stan model for either Linear Regression or Logistic Regression and returns the summary of the fit.

---

* `fit_linear_regression_ME` and `fit_logistic_regression_ME`

  + Required Inputs:
    - **model**: Compiled Stan model for the corresponding regression type.
    - **N**: Number of observations.
    - **D**: Number of covariates, excluding the column with measurement noise.
    - **x_meas**: Input measured independent variable vector with the presence of measurement error".
    - **x_in**: Input matrix x_in for the additional D covariates, with dimensions N by D.
    - **y**: Dependent variable.
    - **a**: Coefficient parameter between true data and observed data *x_meas* subjected to measurement noise.
    - **tau**: parameter that depicts the measurement noise between true and observed data *x_meas*.
  
  + Purpose:
    Both functions fit the provided Bayesian measurement error correction model for linear regression or logistic regression and return a summary of the fit. The functions are particularly useful when dealing with scenarios where the independent variables are subject to measurement noise, allowing for more accurate parameter estimates and inference.

---

* `fit_tau`
  - Required Inputs:
    + **model**: Compiled Stan model for Tau.
    + **N**: Number of observations.
    + **Y**: Dependent variable.
    + **Yp**: Measured dependent variable.
    + **a**: Coefficient parameter.
  - Purpose: This function fits the provided Tau Stan model and returns the summary of the fit.

---

* `load_stan_models`
  - Required Inputs: None.
  - Purpose: This function loads the Stan models for various regression types, the measurement error correction models, and the measurement noise estimation model to find parameter *tau*, and provide a list of compiled Stan models.



## Examples of BayesMEModel Application on a Simulated Dataset

In this example, we utilized a synthetic dataset included in the package, consisting of 10,000 samples. Each sample comprises a pair of phenotype values, where "Y" represents the true data, and "Yp" represents the data including measurement noise. The objective is to discern the relationship between the "Y" phenotype and another phenotype "Z" by employing "Yp" as a substitute.

### Load the necessary packages and the dataset.

```{r}
library(dplyr)
library('rstan')
options(mc.cores = parallel::detectCores())
rstan_options(auto_write = TRUE)

csv_file <- system.file("rmd", "Y_Y_p.csv", package = "BayesMEModel")
raw_data <- read.csv(csv_file)
Y = raw_data$Y
Y_p = raw_data$Y_p
```

### Load all available Stan models in the package for future use.

```{r}
model_list <- load_stan_models()
```

In this analysis, we considered two types of regression: linear regression and logistic regression.

For linear regression, in this example, we considered a simple case with only one covariate Y/Yp. 

1. Simulate Z with a fixed `$\gamma$` value. 

```{r}
eps = rnorm(10000)
gamma = 0.1
Z <- Y * gamma + eps
```

2. Fit a linear regression model to regress Z on Y.

```{r}
x_in = cbind(Y)
Y_fit <- fit_linear_regression(model_list$LinReg, N=10000, D = 1, x = x_in, y = Z)
summary(Y_fit, pars = "beta")[[1]]
```

Upon examining the model's results, we observed an estimated coefficient of 0.1034688, indicating the relationship between phenotype Z and Y.

3. Fit a linear regression model to regress Z on Yp.

```{r}
x_in = cbind(Y_p)
Yp_fit <- fit_linear_regression(model_list$LinReg, N=10000, D = 1, x = x_in, y=Z)
summary(Yp_fit, pars = "beta")[[1]]
```

When fitting the regression model using Yp, which incorporates measurement error, we observe attenuation bias, resulting in a reduced estimated beta of 0.06706846. Our objective is to correct this bias.

4. Fit a linear regression measurement error correction model by regressing Z on Yp.

```{r}
est_a <- lm(Y_p ~ Y)
a <- coef(est_a)["Y"]

tau_fit <- fit_tau(model_list$tau, N = 10000, Y = Y, Yp = Y_p, a = a)
tau <- summary(tau_fit, pars = "tau")[[1]][1]

x_in <- matrix(nrow = 10000, ncol = 0)
linregME_fit <- fit_linear_regression_ME(model_list$LinRegME, 
                                         N=10000, D = 0, 
                                         x_meas=Y_p,
                                         x_in = x_in,
                                         y=Z, 
                                         a=a, tau=tau)
summary(linregME_fit, pars = "beta_meas")[[1]]
```

We initially estimated the parameters 'a' and 'tau,' which characterize the relationship between the true data Y and the data with measurement error Yp. Subsequently, we applied the linear regression measurement error correction model, and the results demonstrated a reduction in the absolute error, decreasing from 0.0364 to 0.0196.


In the logistic regression example, we followed a similar procedure, beginning with the simulation of binary output Z.

1. Simulate Z with a fixed `$\gamma$` value. 

```{r}
eps = rnorm(10000)
gamma <- 0.1
log_odds <- Y * gamma
p <- exp(log_odds) / (1+exp(log_odds))
rand_nums <- runif(10000)
Z = as.integer(rand_nums < p)
```

2. Fit a linear regression model to regress Z on Y.

```{r}
x_in = cbind(Y)
Y_fit <- fit_logistic_regression(model_list$LogisticReg, N=10000, D = 1, x = x_in, y=Z)
summary(Y_fit, pars = "beta")[[1]]
```

We observed that the estimated coefficient for Y and Z is 0.09941951.

3. Fit a linear regression model to regress Z on Yp.

```{r}
x_in = cbind(Y_p)
Yp_fit <- fit_logistic_regression(model_list$LogisticReg, N=10000, D = 1, x = x_in, y=Z)
summary(Yp_fit, pars = "beta")[[1]]
```
Using Yp as in the input data, we observed a significant shrinkage effect on the estimated coefficient, reducing it to 0.03298435.

4. Fit a logistic regression measurement error correction model by regressing Z on Yp.

```{r}
est_a <- lm(Y_p ~ Y)
a <- coef(est_a)["Y"]

tau_fit <- fit_tau(model_list$tau, N = 10000, Y = Y, Yp = Y_p, a = a)
tau <- summary(tau_fit, pars = "tau")[[1]][1]

x_in <- matrix(nrow = 10000, ncol = 0)
logisticRegME_fit <- fit_logistic_regression_ME(model_list$LogisticRegME, 
                                                N=10000, D = 0, 
                                                x_meas=Y_p,
                                                x_in = x_in,
                                                y=Z,
                                                a=a, tau=tau)
summary(logisticRegME_fit, pars = "beta_meas")[[1]]
```

After obtaining estimates for 'a' and 'tau,' we applied the logistic regression measurement error correction model. The outcomes illustrated a decrease in absolute error, which reduced from 0.0664 to 0.0385.

Comparing the estimation results between our method and the uncorrected approach, we observed a reduction in the absolute error in both regression model cases. This reduction indicates that the measurement correction model effectively mitigates attenuation bias and provides a more accurate estimate of the relationship between phenotypes when the input data is subject to measurement noise.
