```{r}
library(dplyr)
library('rstan')
options(mc.cores = parallel::detectCores())
rstan_options(auto_write = TRUE)

raw_data <- read.csv(file = 'Y_Y_p.csv')
Y_p = raw_data$Y_p
Y = raw_data$Y
```

## Load Stan models

```{r}
model_list <- load_stan_models()
```

## Linear Regression Example

### simulate linear regression data

```{r}
eps = rnorm(10000)
gamma = 0.1
Z <- Y * gamma + eps
```

### fit linear regression, regressing Z on Y
```{r}
x_in = cbind(Y)
Y_fit <- fit_linear_regression(model_list$LinReg, N=10000, D = 1, x = x_in, y = Z)
summary(Y_fit, pars = "beta")[[1]]
```

### fit linear regression, regressing Z on Yp
```{r}
x_in = cbind(Y_p)
Yp_fit <- fit_linear_regression(model_list$LinReg, N=10000, D = 1, x = x_in, y=Z)
summary(Yp_fit, pars = "beta")[[1]]
```

### find "a" and "tau" between Y and Yp
```{r}
est_a <- lm(Y_p ~ Y)
a <- coef(est_a)["Y"]

tau_fit <- fit_tau(model_list$tau, N = 10000, Y = Y, Yp = Y_p, a = a)
tau <- summary(tau_fit, pars = "tau")[[1]][1]
```

### fit linear regression measurement error correction model, regressing Z on Yp
```{r}
x_in <- matrix(nrow = 10000, ncol = 0)
linregME_fit <- fit_linear_regression_ME(model_list$LinRegME, 
                                         N=10000, D = 0, 
                                         x_meas=Y_p,
                                         x_in = x_in,
                                         y=Z, 
                                         a=a, tau=tau)
summary(linregME_fit, pars = "beta_meas")[[1]]
```


## Logistic Regression Example

### simulate logistic regression data

```{r}
eps = rnorm(10000)
gamma <- 0.1
log_odds <- Y * gamma
p <- exp(log_odds) / (1+exp(log_odds))
rand_nums <- runif(10000)
Z = as.integer(rand_nums < p)
```

### fit logistic regression, regressing Z on Y
```{r}
x_in = cbind(Y)
Y_fit <- fit_logistic_regression(model_list$LogisticReg, N=10000, D = 1, x = x_in, y=Z)
summary(Y_fit, pars = "beta")[[1]]
```

### fit logistic regression, regressing Z on Yp
```{r}
x_in = cbind(Y_p)
Yp_fit <- fit_logistic_regression(model_list$LogisticReg, N=10000, D = 1, x = x_in, y=Z)
summary(Yp_fit, pars = "beta")[[1]]
```

### find "a" and "tau" between Y and Yp
```{r}
est_a <- lm(Y_p ~ Y)
a <- coef(est_a)["Y"]

tau_fit <- fit_tau(model_list$tau, N = 10000, Y = Y, Yp = Y_p, a = a)
tau <- summary(tau_fit, pars = "tau")[[1]][1]
```

### fit logistic regression measurement error correction model, regressing Z on Yp
```{r}
x_in <- matrix(nrow = 10000, ncol = 0)
logisticRegME_fit <- fit_logistic_regression_ME(model_list$LogisticRegME, 
                                                N=10000, D = 0, 
                                                x_meas=Y_p,
                                                x_in = x_in,
                                                y=Z,
                                                a=a, tau=tau)
summary(logisticRegME_fit, pars = "beta_meas")[[1]]
```
